Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit final sample

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{potential central galaxies in less 
    massive halos} as the \nbcg{} sample. 
    Since we have rejected satellites in \redm{} cluster and the satellite 
    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
    sample are very likely to be the central galaxies of

     very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be neglected for the purpose of 
    this work
    .
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%% ------------------------------------------------------------------------------------ %%

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
           \logmh{}$<14.0$.

%          : we select a sample of 164 galaxies at 
%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
%            in $\lambda > 30$ \redm{} clusters. 
%            They represent the central galaxies in very massive halos 
%            (\logmh{}$\geq 14.2$). 
%        \item \nbcg{} sample: after excluding all cluster members from the 
%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
%            $0.3 \leq z \leq 0.5$. 
%            After applying an additional \mstar{} cut (see Section 
%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
%            halos with \logmh{}$<14.0$.  
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %%     
    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
    \label{ssec:s82}

    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
    DSouza2014, DSouza2015, Bernardi2016a}). 
    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
    As can be seen from this figure, our careful 1-D approach recovers more flux 
    in massive galaxies than \texttt{cModel}. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
    and also reflects the fact that more massive ETGs tend to have more extended 
    stellar mass distributions (e.g. \citealt{Graham2003}). 
    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end and slightly modifies the high-mass slope. 
    %The impact of missing flux is most prominent for the \rbcg{} sample.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate the HSC massive galaxies into the central galaxies living 
          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line). 
          The uncertainty of distribution using \mtot{} is shown in grey shaded 
          region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Even with deep HSC images, it is non trivial to clearly define and measure the
    ``total'' \mstar{} for these massive systems. 
    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture a the majority of 
    the stellar mass. 
    However, even though we extend to 100 kpc, there is no evidence that the profile 
    drops to zero on these scales. 
    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
    For this, we integrate the \mden{} profiles out to the detection limit in 
    surface brightness profile that is defined by the background noise.
    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
    difference of about ${\sim}0.04$ dex. 
    The left hand side of Fig \ref{fig:discussion_2} shows differences between \mtot{}
    and \mmax{}. 
    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
    of the stellar envelope. 
    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
    uncertainty on \mmax{} is larger. 
    However, we have checked that none of our results are changed by replacing \mtot{} 
    via \mmax{}.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:discussion_2} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:discussion_2} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

>>>>

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{potential central galaxies in less 
    massive halos} as the \nbcg{} sample. 
    Since we have rejected satellites in \redm{} cluster and the satellite 
    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
    sample are very likely to be the central galaxies of their own dark matter halos.
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%% ------------------------------------------------------------------------------------ %%

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item With the help of the \redm{} cluster catalog, we further select 
            candidates of massive central galaxies in a range of \mhalo{}
            We broadly divide the sample into the central galaxies living in halos
            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
    \end{itemize}

    To discuss the mass-dependence of galaxy structure, we will combine the \rbcg{}
    and \nbcg{} samples and group them into three bins of \mtot{}.  
    In this work, we will only separately discuss the \rbcg{} and \nbcg{} samples 
    when we look into the impact of \mstar{} definition on the SMF in Section 
    \ref{ssec:smf}. 
    We will carefully look into the structural differences between the central galaxies 
    from these two samples later (Huang\etal~in prep.).  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate the HSC massive galaxies into the central galaxies living 
          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line). 
          The uncertainty of distribution using \mtot{} is shown in grey shaded 
          region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
    \label{ssec:smf}

    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
    ``total'' stellar mass.

    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
    DSouza2014, DSouza2015, Bernardi2016a}). 
    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
    As can be seen from this figure, our careful 1-D approach recovers more flux 
    in massive galaxies than \texttt{cModel}. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
    and also reflects the fact that more massive ETGs tend to have more extended 
    stellar mass distributions (e.g. \citealt{Graham2003}). 
    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end and slightly modifies the high-mass slope. 
    %The impact of missing flux is most prominent for the \rbcg{} sample.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.

        Even with deep HSC images, it is non trivial to clearly define and measure the
    ``total'' \mstar{} for these massive systems. 
    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture a the majority of 
    the stellar mass. 
    However, even though we extend to 100 kpc, there is no evidence that the profile 
    drops to zero on these scales. 
    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
    For this, we integrate the \mden{} profiles out to the detection limit in 
    surface brightness profile that is defined by the background noise.
    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
    difference of about ${\sim}0.04$ dex. 
    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
    and \mmax{}. 
    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
    of the stellar envelope. 
    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
    uncertainty on \mmax{} is larger. 
    However, we have checked that none of our results are changed by replacing \mtot{} 
    via \mmax{}.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

@@

@@

@@

    Even with deep HSC images, it is non trivial to clearly define and measure the
    ``total'' \mstar{} for these massive systems. 
    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture a the majority of 
    the stellar mass. 
    However, even though we extend to 100 kpc, there is no evidence that the profile 
    drops to zero on these scales. 
    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
    For this, we integrate the \mden{} profiles out to the detection limit in 
    surface brightness profile that is defined by the background noise.
    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
    difference of about ${\sim}0.04$ dex. 
    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
    and \mmax{}. 
    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
    of the stellar envelope. 
    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
    uncertainty on \mmax{} is larger. 
    However, we have checked that none of our results are changed by replacing \mtot{} 
    via \mmax{}.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.
